### 2019-12-27 paper.rmd
add some implications for software developers

### Is the missing data mechanism reported?                                                                                                                                                                                                         
### Is a description provided of what variables are related to attrition/missing data?

@@

>>>>

### Is the missing data mechanism reported?

### Is a description provided of what variables are related to attrition/missing data?

@@

# Implications

A step away from the tutorial side of this work, we wish to note some implications 
for the developers of statistical software for psychological scientists.

First, we note that developing a tool that emphasized both rigor and access has
been, so far, well-received. This suggests that there is an audience (or a
market) for tools to carry out sophisticated tools that may be otherwise
out-of-reach. Tools do not need to be hard to use, a point made by developers
of, for example, tools to carry out highly-sophisticated Bayesian methods using
the most cutting-edge tools (Makowski et al., 2019, Burkner, 2018). We think
that tidyLPA speaks to this, too.

Another implication concerns how we developed tidyLPA. We used a modern software
development workflow, including git/GitHub, a suite of tests, and continuous
integration tools. We also note that we emphasized communicating that we were
developing the software; when it was updated; and how we made major updates.
